---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# noderank

<!-- badges: start -->
<!-- badges: end -->

noderank maps differential gene expression results 
    onto an established network of protein-protein associations and 
    employs network analysis methods to select a prioritized list of 
    important nodes. For data in which the mechanism of perturbation is 
    known, each ranked list result is scored by the position of the 
    causal gene. 

## Installation

You can install the released version of noderank from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("noderank")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(noderank)
## basic example code
```

## A roadmap for noderank:

Starting material: differential gene expression analysis results, i.e. the output
of topTable() from *limma* or results() from *DESeq2*. 

1. 

```{r cars}
# summary(cars)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
# plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub!
